# squaring the data to correctly display dataset
```{r}
dim(seattleTop_2)
```

# checking out the column names--making sure there are no spaces or weird characters
```{r}
names(seattleTop_2)
```
# moving the column "name" to get a square matrix
```{r}
row.names(seattleTop_2)=seattleTop_2$name
seattleTop_2$name=NULL
dim(seattleTop_2)
```
# converting the data frame into a matrix
```{r}
seattleTop_2_Mx=as.matrix(seattleTop_2)
```

# ensuring that I have the correct package installed, then creating a network with igraph
```{r}
library(igraph)
EliteNet=graph.adjacency(seattleTop_2_Mx,mode="undirected",weighted=NULL)
```

# didn't have igraph, so I installed it and reran the above code
```{r}
install.packages("igraph")
```
# checking how many nodes are in my network (aka individual users)
```{r}
vcount(EliteNet)
```

# counting the number of edges within my dataset, or how many boundaries connect to another
```{r}
ecount(EliteNet)
```

# plotting my network to see what it looks like
```{r}
plot.igraph(EliteNet,
            vertex.color='lightyellow',
              edge.color='lightgreen')
```

# can every node connect to another node? 
# yes (see below). so, I do not need to extract and analyze a component with max nodes.
```{r}
is_connected(EliteNet)
```

# measuring the interconnectivity of my network, i.e., if all the users follow one another 
```{r}
graph.density(EliteNet)
```

# measuring the longest path from one user to another. it is 3, meaning that the most users one user would have go through to the farthest one is 3. 
```{r}
diameter(EliteNet)
```

# which pair has represents the diameter? they are the least connected.
```{r}
farthest_vertices(EliteNet)
```
# what is the average shortest path a user takes to reach another?
```{r}
average.path.length(EliteNet)
```

# what is the probability that two users who share a follower/following are connected to another similar follower
```{r}
transitivity(EliteNet)
```

# do users connect with other users with similar characteristics? 
```{r}
assortativity_degree(EliteNet)
```

# exploring network actors
# closeness displays the closeness factor from one vertex to another. the larger the closeness, the more quickly one user can share information with another user. 
# betweenness shows the number of times a user lies on the shortest path to another user.
# eigenvector tells how influential (or better connected) a vertex is to another vertex who is also well connected.
```{r}
rounding=3
degr=round(degree(EliteNet,normalized=T),rounding)
close=round(closeness(EliteNet,normalized=T),rounding)
betw=round(betweenness(EliteNet,normalized=T),rounding)
eigv=round(eigen_centrality(EliteNet,scale=F)$vector,rounding)

DFCentrality=as.data.frame(cbind(close,betw,eigv),stringsAsFactors = F)
names(DFCentrality)=c('Closeness','Betweenness','Eigenvector')
```

# then, I make the table showing those relationships!
```{r}
DFCentrality$Person=row.names(DFCentrality)
row.names(DFCentrality)=NULL
head(DFCentrality)
```
# I notice a mistake I made earlier--dropping the "Person" column
```{r}
df2=DFCentrality[,-5]
```

# corrected
```{r}
df2
```
# renaming the column from "person" to "Username" to better reflect the dataset
```{r}
names(df2)[4]='Username'
```

# What does it look like now? 
```{r}
df2
```

# ok, now that the dataset is corrected and we have mapped out the relationships... let's see the final product.
```{r}
library(ggplot2)
ggplot(df2, aes(x=Betweenness, y=Closeness)) + 
    theme_classic() +
    geom_text(aes(label=Username,color=Eigenvector)) +
    scale_colour_gradient(low = "orange", high = "black")
```
# it looks like DaveParkerSEA and toddbishop are the most influential and well-connected users in the dataset.

# can this network be disconnected?
```{r}
vertex_connectivity(EliteNet)
```
# no

# regardless, I am curious to see what the code will say if I ask it who can disconnect the network. I know it will not give me a username.
```{r}
(thecut=articulation.points(EliteNet))
```
# it did not identify anyone, and gave me a 0 answer. cool!

# fin!